---
title: "Identifable support WIP figures"
date: "2019-04-19"
output: html_document
editor_options: 
  chunk_output_type: console
---
  
## Data setup   
```{r setup, include=FALSE}

## By defult, show code for all chunks in the knitted document,
## as well as the output. To override for a particular chunk
## use echo = FALSE in its options.
knitr::opts_chunk$set(echo = TRUE) 

## Set the default size of figures
knitr::opts_chunk$set(fig.width=8, fig.height=5)  

## Load the libraries we will be using
library(gapminder)
library(here)
library(socviz)
library(tidyverse)
library(formattable)

## Import data

library(readxl)
r <- read_excel("complied results.xlsx")
library(dplyr)
r$`Home Support` <- recode(r$`Home Support`, "Lives alone, can ID support" = "Can ID support")
r$`Home Support` <- recode(r$`Home Support`, "Lives alone, cannot ID support" = "Cannot ID support")

## figure settings
sachin_theme <- theme_bw()+
        theme(
          panel.background = element_blank(), 
          axis.line = element_line(colour = "grey75"),
          panel.border = element_blank(),
          panel.grid.major.x = element_blank(),
          panel.grid.minor.x = element_blank(),
          panel.grid.major.y = element_line(color = "grey", linetype = "dotted" ),
          panel.grid.minor.y = element_blank(),
          legend.position = "none", 
          axis.title=element_text(size=10)
          )

sachin_theme_leg <- theme_bw()+
        theme(
          panel.background = element_blank(), 
          axis.line = element_line(colour = "grey75"),
          panel.border = element_blank(),
          panel.grid.major.x = element_blank(),
          panel.grid.minor.x = element_blank(),
          panel.grid.major.y = element_line(color = "grey", linetype = "dotted" ),
          panel.grid.minor.y = element_blank(),
          legend.position = "top", 
          legend.title = element_blank(),
          axis.title=element_text(size=10)
          )


```



## Figure 1: Conceptual diagram

```{r concept}
library("grid")


# EXAMPLE 1 - NO EFFECT
data_sx <- c(1,1.4,15,15.4)
data_shock <- c("No shock", "No shock", "Shock", "Shock")
data_level <- c("High support", "Low support", "High support", "Low support")

data.concept <- data.frame("Scenario" = data_scenario, "Outcome" = data_sx, "Stressor" = data_shock, "Support" = data_level)

data.concept$Support <- factor(data.concept$Support, levels = c("Low support", "High support"))


fig.noeffect <- 
    ggplot(data = data.concept, aes(y=Outcome, x=Stressor, group=Support)) +
    geom_point(aes(color = Support), size = 3) +
    geom_line(aes(color = Support), size = 1) +
    scale_y_continuous(limits = c(0,16),
                        breaks = c(1,15),
                        labels = c("Low", "High")) +
    ggtitle("No effect") + 
  sachin_theme_leg

# EXAMPLE 1 - MAIN EFFECT
data_sx <- c(1,5,11,15)
data_shock <- c("No shock", "No shock", "Shock", "Shock")
data_level <- c("High support", "Low support", "High support", "Low support")

data.concept <- data.frame("Scenario" = data_scenario, "Outcome" = data_sx, "Stressor" = data_shock, "Support" = data_level)

data.concept$Support <- factor(data.concept$Support, levels = c("Low support", "High support"))

fig.maineffect <-
  ggplot(data = data.concept, aes(y=Outcome, x=Stressor, group=Support)) +
    geom_point(aes(color = Support), size = 3) +
    geom_line(aes(color = Support), size = 1) +
    scale_y_continuous(limits = c(0,16),
                        breaks = c(1,15),
                        labels = c("Low", "High")) +
    ggtitle("Main effect") + 
  sachin_theme_leg

# EXAMPLE 2 - BUFFERING EFFECT
data_sx <- c(1,1,8,15)
data_shock <- c("No shock", "No shock", "Shock", "Shock")
data_level <- c("High support", "Low support", "High support", "Low support")

data.concept <- data.frame("Scenario" = data_scenario, "Outcome" = data_sx, "Stressor" = data_shock, "Support" = data_level)

data.concept$Support <- factor(data.concept$Support, levels = c("Low support", "High support"))

fig.bufferingeffect <-
  ggplot(data = data.concept, aes(y=Outcome, x=Stressor, group=Support)) +
    geom_point(aes(color = Support), size = 3) +
    geom_line(aes(color = Support), size = 1) +
    scale_y_continuous(limits = c(0,16),
                        breaks = c(1,15),
                        labels = c("Low", "High")) +
    ggtitle("Buffering effect") + 
  sachin_theme_leg

library(gridExtra)
grid.arrange(fig.noeffect, fig.maineffect, fig.bufferingeffect, ncol = 3)

```

## Table 1: Patient characteristics - First 

```{r t1}

library(haven)
t1 <- read_sas("C:/Users/sachi/Box Sync/HRS/processed data/analytic_long_2020_05_08_first.sas7bdat", 
    NULL)
t1$AGE <- as.numeric(t1$AGE)

myVars <- c("AGE","RAFEMALE", "RARACEM", "RAHISPAN", "married", "HSGRAD", "INC_ABV_MED", "poorhealth",
		        "PAIN", "BADVISION",  "BADHEARING", "HIGHBP", "DIABETES", "CANCER",  "LUNGD",  
		        "HEARTD",  "STROKE", "ARTHRITIS", "DEPRESSION", "SMOKING", "BEDDIFF", "BATHDIFF",
		        "DRESSDIFF", "EATDIFF",	"TOILTDIFF", "WALKDIFF", "COG", "PROXY")

catVars <- c("RAFEMALE", "RARACEM", "RAHISPAN", "married", "HSGRAD", "INC_ABV_MED", "poorhealth",
		        "PAIN", "BADVISION",  "BADHEARING", "HIGHBP", "DIABETES", "CANCER",  "LUNGD",  
		        "HEARTD",  "STROKE", "ARTHRITIS", "DEPRESSION", "SMOKING", "BEDDIFF", "BATHDIFF",
		        "DRESSDIFF", "EATDIFF",	"TOILTDIFF", "WALKDIFF", "COG", "PROXY")

not_nl <- c("AGE")

library(labelled)
var_label(t1) <- list(AGE = "Age", RAFEMALE = "Female", RARACEM = "Race", RAHISPAN = "Hispanic ethnicity", 
                     married = "Marital status", HSGRAD = "High school graduate",
                     INC_ABV_MED = "Net worth less than median", poorhealth = "Fair or poor self reported health", 
                     PAIN = "Significant pain", BADVISION = "Visual impairment", 
                     BADHEARING = "Hearing impairment", HIGHBP = "Hypertension",
                     DIABETES = "Diabetes", CANCER = "Cancer (excluding minor skin cancer)",
                     LUNGD = "Lung disease", HEARTD = "Heart disease", STROKE = "Stroke", ARTHRITIS = "Arthritis",
                     SMOKING = "Ever tobacco use", BEDDIFF = "Difficulty getting out of bed", WALKDIFF = "Difficulty walking",
                     DRESSDIFF = "Difficulty dressing", BATHDIFF = "Difficulty bathing", EATDIFF = "Difficulty dating", 
                     TOILTDIFF = "Difficulty toileting", COG = "Cognition", PROXY = "Proxy interview")
library(tableone)
tab2 <- CreateTableOne(vars = myVars, strata = "nosupport", data = t1, factorVars = catVars)
tab2a <- print(tab2, nonnormal = not_nl, catDigits = 0, contDigits = 1, varLabels = TRUE, format = "fp", test = T, noSpace = TRUE, dropEqual = TRUE, printToggle = TRUE, quote = T)
 # tab2b <- tab2a[,1:3]
 # print(tab2b, quote = FALSE)




```





## Table 1: Patient characteristics - All

```{r t1full}

library(haven)
library(tidyverse)
t1.full <- read_sas("C:/Users/sachi/Box Sync/HRS/processed data/analytic_long_2020_05_08_no_miss.sas7bdat", 
    NULL)

t1.full$AGE <- as.numeric(t1.full$AGE)


myVars <- c("AGE","RAFEMALE", "RARACEM", "RAHISPAN", "married", "HSGRAD", "INC_ABV_MED", "poorhealth", "PAIN",  "HIGHBP", "DIABETES", "CANCER",  "LUNGD", "HEARTD",  "STROKE", "ARTHRITIS", "DEPRESSION", "SMOKING", "ADLDIFF", "BEDDIFF", "BATHDIFF", "DRESSDIFF", "EATDIFF",	"TOILTDIFF", "WALKDIFF", "COG", "BADVISION",  "BADHEARING", "PROXY")

catVars <- c("RAFEMALE", "RARACEM", "RAHISPAN", "married", "HSGRAD", "INC_ABV_MED", "poorhealth",
"PAIN", "HIGHBP", "DIABETES", "CANCER",  "LUNGD", "HEARTD",  "STROKE", "ARTHRITIS", "DEPRESSION", "SMOKING", "ADLDIFF", "BEDDIFF", "BATHDIFF", "DRESSDIFF", "EATDIFF",	"TOILTDIFF", "WALKDIFF", "COG", "BADVISION", "BADHEARING", "PROXY")

not_nl <- c("AGE")

library(labelled)
var_label(t1.full) <- list(AGE = "Age", RAFEMALE = "Female", RARACEM = "Race", RAHISPAN = "Hispanic ethnicity", married = "Marital status", HSGRAD = "High school graduate", INC_ABV_MED = "Net worth less than median", poorhealth = "Fair or poor self reported health", PAIN = "Significant pain", BADVISION = "Visual impairment", BADHEARING = "Hearing impairment", HIGHBP = "Hypertension",DIABETES = "Diabetes", CANCER = "Cancer (excluding minor skin cancer)", LUNGD = "Lung disease", HEARTD = "Heart disease", STROKE = "Stroke", ARTHRITIS = "Arthritis", DEPRESSION = "Depression", SMOKING = "Ever tobacco use", ADLDIFF = "Difficulty with any ADL", BEDDIFF = "Difficulty getting out of bed", WALKDIFF = "Difficulty walking", DRESSDIFF = "Difficulty dressing", BATHDIFF = "Difficulty bathing", EATDIFF = "Difficulty eating", TOILTDIFF = "Difficulty toileting", COG = "Cognition", PROXY = "Proxy interview")

library(tableone)
tab2 <- CreateTableOne(vars = myVars, strata = "nosupport", data = t1.full, factorVars = catVars)
tab2a <- print(tab2, nonnormal = not_nl, catDigits = 0, contDigits = 0, varLabels = TRUE, format = "fp", test = T, noSpace = TRUE, dropEqual = TRUE, printToggle = TRUE, quote = T)
 # tab2b <- tab2a[,1:3]
 # print(tab2b, quote = FALSE)




```









## Figure 2: Unadjusted outcomes

```{r unadj, echo = FALSE, fig.width= 6, fig.height=4}

library(readr)
u <- read_csv("C:/Users/sachi/Box Sync/HRS/results/Unadjusted margins support x outcomes.csv")
u$outcome <- factor(u$outcome, levels = c("ADL", "NH", "Died"))

library(dplyr)
u.1 <- u %>% 
          filter(model == "Logistic") %>%
          mutate(Support = ifelse(nosupport == 1, "No support", "Support")) %>%
          mutate(outcome=recode(outcome,
                                  ADL = "ADL dependency",
                                  NH = "Nursing home stay",
                                  Died = "Deceased"))

library(ggplot2)
dodge <- position_dodge(width = 0.2)

fig.mainoutcome_unadj <- ggplot(data = u.1, 
        aes(x = outcome, y = `_mu`,  color = Support)) +
        geom_point(size = 3, position = dodge) + 
        geom_errorbar(
            aes(ymin=Lower, ymax = Upper), 
            width = 0.05,
            size = 1,
            position = dodge) +
        scale_y_continuous(
            name = "Likelihood", 
            labels = scales::percent_format(accuracy = 1)
            ,
            limits = c(0.0, 0.14), 
            breaks = c(seq(from=0.00, to =0.14, by =0.02))
            )+
        xlab("Outcome") +
        sachin_theme_leg  
fig.mainoutcome_unadj 
         

setwd("C:/Users/sachi/Box Sync/HRS/results/figures")
fig.mainoutcome_unadj
ggsave("F2 - support x outcomes unadjusted.png", width = 6, height = 4)

```



## F3: Adjusted outcomes
```{r adj, echo = FALSE, fig.width= 6, fig.height=4}

library(readr)
v <- read_csv("C:/Users/sachi/Box Sync/HRS/results/Adjusted margins support x outcomes.csv")
v$outcome <- factor(v$outcome, levels = c("ADL", "NH", "Died"))

library(dplyr)
v.1 <- v %>% 
          filter(model == "Logistic") %>%
          mutate(Support = ifelse(nosupport == 1, "No support", "Support")) %>%
          mutate(outcome=recode(outcome,
                                  ADL = "ADL dependency",
                                  NH = "Nursing home stay",
                                  Died = "Deceased"))

library(ggplot2)
dodge <- position_dodge(width = 0.2)

fig.mainoutcome_adj <- ggplot(data = v.1, 
        aes(x = outcome, y = `_mu`,  color = Support)) +
        geom_point(size = 3, position = dodge) + 
        geom_errorbar(
            aes(ymin=Lower, ymax = Upper), 
            width = 0.05,
            size = 1,
            position = dodge) +
        scale_y_continuous(
            name = "Adjusted likelihood", 
            labels = scales::percent_format(accuracy = 1)
            ,
            limits = c(0.0, 0.14), 
            breaks = c(seq(from=0.00, to =0.14, by =0.02))
            )+
        xlab("Outcome") +
        sachin_theme_leg  

fig.mainoutcome_adj

setwd("C:/Users/sachi/Box Sync/HRS/results/figures")
fig.mainoutcome_adj
ggsave("F3 - support x outcomes adjusted.png", width = 6, height = 4)

```




##Figure 4: Adjusted analyses, stratified by health shock
* Adjusted for age, gender, race, education, income, pain, visual impairment, hearing impairment, hypertention, cancer diagnosis, lung disease, heart diease, stroke, arthritis, cognitive impairment, ADL difficulty
* stratified by health shock, defined as hosptial stay >= 2 days, new cancer diagnosis, new stroke, new heart attack

```{r shock, echo=FALSE}

library(readr)
setwd("C:/Users/sachi/Box Sync/HRS/results/figures")

w <- read_csv("C:/Users/sachi/Box Sync/HRS/results/Adjusted outcomes support x shock.csv")
w$Outcome <- factor(w$Outcome, levels = c("ADL dependency", "Nursing home stay", "Deceased"))
w$SHOCK <- factor(w$`Health shock`, levels =c("No health shock", "Health shock"))
w$Support <- factor(w$Support, levels =c("No support", "Support"))
w$label <- ifelse(is.na(w$`Average marginal effect (95% CI)`), NA, (paste("Difference (95% CI): \n", w$`Average marginal effect (95% CI)`)))
dodge <- position_dodge(0.01)

r.shock_d <- w %>% filter(Outcome == "Deceased") 
r.shock_d$nudge <- c(NA, -0.025, NA, -0.04)

fig.shock_deceased <- ggplot(data = r.shock_d, aes(y=`Predicted Value`, x=SHOCK, group=Support, label=label)) +
                          geom_point(aes(color =Support), 
                                     size = 3, 
                                     position = dodge,
                                     alpha = 1) +
                          geom_line(aes(color = Support), 
                                    size = 1, 
                                    position = dodge, 
                                    alpha = 1) +
                          geom_errorbar(
                              aes(ymin=Lower, ymax = Upper, color = Support), 
                              width = 0.05,
                              size = 1,
                              position = dodge) +
                          scale_y_continuous(
                              name = "Likelihood of death", 
                              labels = scales::percent_format(accuracy = 1),
                              limits = c(0.0, 0.2), 
                              breaks = c(seq(from=0.0, to =0.2, by =0.02))
                              )+
                          scale_x_discrete(
                              name =""
                          ) +
                          sachin_theme_leg +
                          geom_text(size = 3.0, nudge_y = r.shock_d$nudge)+
                          ggtitle("C. Deceased")

fig.shock_deceased
ggsave("F4 Shock - Death RR.png", width = 6, height = 4)

## ADL

r.shock_adl <- w %>% filter(Outcome == "ADL dependency") 
r.shock_adl$nudge <- c(NA, -0.025, NA, -0.045)
fig.shock_adl <- ggplot(data = r.shock_adl, aes(y=`Predicted Value`, x=SHOCK, group=Support, label=label)) +
                          geom_point(aes(color =Support), 
                                     size = 3, 
                                     position = dodge,
                                     alpha = 1) +
                          geom_line(aes(color = Support), 
                                    size = 1, 
                                    position = dodge, 
                                    alpha = 1) +
                          geom_errorbar(
                              aes(ymin=Lower, ymax = Upper, color = Support), 
                              width = 0.05,
                              size = 1,
                              position = dodge) +
                          scale_y_continuous(
                              name = "Likelihood of ADL dependency", 
                              labels = scales::percent_format(accuracy = 1),
                              limits = c(0.0, 0.2), 
                              breaks = c(seq(from=0.0, to =0.2, by =0.02))
                              )+
                          scale_x_discrete(
                              name =""
                          ) +
                          sachin_theme_leg +
                          geom_text(size = 3, nudge_y = r.shock_adl$nudge)+
                          ggtitle("A. ADL dependency")

 fig.shock_adl
ggsave("F4 Shock - ADL RR.png", width = 6, height = 4)
 
 
 
## NH

r.shock_nh <- w %>% filter(Outcome == "Nursing home stay") 
r.shock_nh$nudge <- c(NA, -0.01, NA, -0.035)
r.shock_nh$label <- ifelse(r.shock_nh$label == "Difference (95% CI): \n 0.5% (-0.1% to 1.1%)", "Difference (95% CI): 0.5% (-0.1% to 1.1%)", r.shock_nh$label )

fig.shock_nh <- ggplot(data = r.shock_nh, aes(y=`Predicted Value`, x=SHOCK, group=Support, label=label)) +
                          geom_point(aes(color =Support), 
                                     size = 3, 
                                     position = dodge,
                                     alpha = 1) +
                          geom_line(aes(color = Support), 
                                    size = 1, 
                                    position = dodge, 
                                    alpha = 1) +
                          geom_errorbar(
                              aes(ymin=Lower, ymax = Upper, color = Support), 
                              width = 0.05,
                              size = 1,
                              position = dodge) +
                          scale_y_continuous(
                              name = "Likelihood of nursing home stay", 
                              labels = scales::percent_format(accuracy = 1),
                              limits = c(0.0, 0.2), 
                              breaks = c(seq(from=0.0, to =0.2, by =0.02))
                              )+
                          scale_x_discrete(
                              name =""
                          ) +
                          sachin_theme_leg +
                          geom_text(size = 3, nudge_y = r.shock_nh$nudge)+
                          ggtitle("B. Nursing home stay")

 fig.shock_nh





fig.shock_nh
ggsave("F4 Shock - NH RR.png", width = 6, height = 4)

library(gridExtra)
fig.all <- grid.arrange(fig.shock_adl, fig.shock_nh, fig.shock_deceased, ncol = 3)

```